Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-03-15 products/manuscript/Manuscript.qmd
Updated Predictor Variables table.

@@

```{r}
# Load libraries
library(knitr)
library(kableExtra)
library(dplyr)

# Descriptive statistics for numeric variables
pred_summary <- mydata %>%
  summarise(across(c(wra, pct_currentlymarried,pct_nevermarried,rate_matdeaths, rate_matdeaths_upreg, rate_matdeaths_abs), mean, sd))

# Descriptive statistics for categorical variable (assuming region is a factor)
summary_factor <- mydata %>%
  group_by(region) %>%
  summarise(n = n())

# Combine into a single dataframe
summary_pred <- rbind(
  pred_summary %>% summarise(Variable = "pct_upreg_sarc", ., .names = quote(names(.))),
  pred_summary %>% select(-pct_upreg_sarc),
  summary_factor %>% summarise(Variable = "region", n)
)

# Create table 
kable(summary_pred, caption = "Table Depicting Predictor Variables", booktabs = TRUE) %>%
  kable_styling(full_width = F, font_size = 10) %>%
  column_def(widths = c(200, 150, 150))

>>>>

The predictor variables will include:
1. The total number of people women using each type of birth control standardized by population size 2. Region
3. Percentage of women currently married
4. Percentage of women never married
5. Total rate of maternal deaths
6. Rate of maternal deaths due to unintended pregnancy 
7. Rate of maternal deaths due to abortion.

@@

```{r}
# Load libraries

library(kableExtra)

# Selecting variables
selected_variables <- mydata[c("pct_upreg_sarc", "region", "wra", "pct_currentlymarried", "pct_nevermarried","rate_matdeaths", "rate_matdeaths_upreg", "rate_matdeaths_abs")]

# Converting region from factor to numeric
selected_variables$region <- as.numeric(as.factor(selected_variables$region))

# Create table 
kable(selected_variables, caption = "Table Depicting Predictor Variables", booktabs = TRUE) %>%
  kable_styling(full_width = F, font_size = 10)
